---
title: "Curriculum Vitae"
author: "Erik Marsja"
date: "`r Sys.Date()`"
output:
  pdf_document:
    keep_tex: yes
    latex_engine: pdflatex
    template: template.tex
  html_document:
    df_print: paged
  word_document: default
email: erik@marsja.se
fontawesome: yes
geometry: margin=1.2in
github: marsja
lang: Swedish, English
phone: +4670-36 33 662
subparagraph: yes
address: Kandidatvägen 1, SE-907 33 Umeå, Sweden
web: www.marsja.se
CV: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Education

2017 \hspace{1.5cm} \textbf{Ph.D. in Psychology}\vspace{1mm}

\hrule

\begin{changemargin}{2.3cm}{2.4cm}

Department of Psychology, Umeå University.

\textbf{Thesis title}: Attention capture by sudden and unexpected changes: a multisensory perspective. 

Available from the DiVA Database: \sloppy http://umu.diva-portal.org/smash/record.jsf?pid=diva2%3A1156775

\textbf{Supervisors}: Associate Professor Jessica K. Ljungberg, Professor Gregory Neely, \& Dr. Patrik Hansson
\end{changemargin}

2012 \hspace{1.5cm}\textbf{M.Sc. in Cognitive Science}\vspace{1mm}

\hrule
\begin{changemargin}{2.3cm}{2.4cm}

Department of Psychology, Umeå University.

\textbf{Thesis title}: Attention Capture: The Impact of Change in Spatial Sound Source on Behavior. 
    
\textbf{Supervisor}: Associate Professor Jessica K. Ljungberg
\end{changemargin}
    
2011 \hspace{1.5cm}\textbf{B.Sc. in Cognitive Science}\vspace{1mm}
\hrule

\begin{changemargin}{2.3cm}{2.4cm}

Department of Psychology, Umeå University.

\textbf{Thesis title}:  Attention Capture: Studying the Distracting Effect of One’s Own Name.

Available from DiVA Database: \sloppy http://urn.kb.se/resolve?urn=urn:nbn:se:umu:diva-46607.
    
\textbf{Supervisor}: Associate Professor Jessica K. Ljungberg
\end{changemargin}

## Employment

Jan 2019 - \hspace{0.50cm}\textbf{Postdoctoral Researcher}\vspace{1mm}

\hrule
\begin{changemargin}{2.3cm}{2.4cm}

Division for Disability Resarch, Department of Behavioural Sciences and Learning (IBL), Linköping University.

Analysing data from a large database (i.e., n200) and preparing manuscripts in the field of cognitive hearing science. Responsible for arranging the monthly \href{https://liu.se/linnecentrum-head/en}{HEAD} seminar series. This includes contacting national, and international, researchers, booking flights, hotels, as well as setting up equipment for online streaming.

\end{changemargin}


Aug 2018 -

Oct 2018\hspace{0.75cm}\textbf{Postdoctoral Research Assistant}\vspace{1mm}

\hrule
\begin{changemargin}{2.3cm}{2.4cm}

Department of Psychology, Umeå University.

\textbf{Project}: How does humans perception of safety differ in a broken communication chain compared to an unbroken communication chain? 

Literature study commissioned by SOS Alarm, an emergency agency (e.g., public-safety answering point), with the results dissiminating in a report.

\end{changemargin}

Oct 2012 -

June 2018\hspace{0.75cm}\textbf{PhD Student and Teaching Assistant}\vspace{1mm}

\hrule
\begin{changemargin}{2.3cm}{2.4cm}

Department of Psychology, Umeå University.

Planning of studies, programming of experiments, literature search, data analysis, scientific communication, and many more. See the section "Teaching responsibilities" for an overview of my pedagogical experience.

\end{changemargin}

June 2011\hspace{0.75cm}\textbf{Undergrad. Research Assistant}\vspace{1mm}

\hrule
\begin{changemargin}{2.3cm}{2.4cm}

Department of Psychology, Umeå University.

Recruitment of participants and data collection.

\end{changemargin}

## Publications

### International peer-reviewed journals

**Marsja**, E., Marsh, J.E., Hansson, P., & Neely, G. (2019). Examining the Role of Spatial Changes in Bimodal and Uni-Modal To-Be-Ignored Stimuli and How They Affect Short-Term Memory Processes. *Frontiers In Psychology*. https://doi.org/10.3389/fpsyg.2019.00299

**Marsja**, E., Neely, G., & Ljungberg, J. K. (2018). Investigating Deviance Distraction and the Impact of the Modality of the To-Be-Ignored Stimuli. *Experimental Psychology, 65(2)*, 61–70. http://doi.org/10.1027/1618-3169/a000390

Ljungberg, K. J., Parmentier, F. B. R., Jones, D. M., **Marsja**, E., & Neely, G. (2014). “What’s in a name?” “No more than when it’s mine own". Evidence from auditory oddball distraction. *Acta Psychologica, 150C*, 161–166. http://dx.doi.org/10.1016/j.actpsy.2014.05.009

### Publications In Preparation/Submitted/Under Revision

Stenbäck, V., **Marsja**, E., Danielsson, H., & Rönnberg, J. (Manuscript in Preparation). Predictors for Performance in Speech Recognition in Noise Tests: Objective and Subjective Outcome Measures

**Marsja**, E. Elbe, P., Sörman, D. (Manuscript in Preparation). Examining the Factor Structure of the Swedish Translation of the Attentional Control Scale and it's relation to objective measures of attention.

Rosa, E., **Marsja**, E., Ljungberg, K.J. (Submitted). Exploring residual capacity: The effectiveness of a vibrotactile warning during increasing levels of mental workload in simulated flight tasks.

Marsh, J.E., Vachon, F., Sörqvist, P., **Marsja**, E., Röer J.P., & Ljungberg, K.J. (Manuscript in Preparation).  Irrelevant vibro-tactile stimuli produce a changing-state effect: Implications for theories of interference in short-term memory.

**Marsja**, E., Neely, G., & Ljungberg, K.J (Manuscript in Preparation). Deviance distraction in the auditory and tactile modalities after repeated exposure: differential aspects of tactile and auditory deviants.


## Conference Presentations

**Marsja**, E., Danielsson, H., Stenbäck, V., Moradi, S., Rönnberg, J. (2019, June). Examining Relationship Amongst Cognition,
Hearing Loss, Age, & Speech in Noise. Cognitive Hearing Science for Communication, Linköping, Sweden. **Poster**.

Stenbäck, V., Moradi, S., **Marsja**, E., Danielsson, H., Rönnberg, J. (2019, June). Logical and auditory inference-making in normally-hearing and hearing-impaired listeners. Cognitive Hearing Science for Communication, Linköping, Sweden. **Poster**.

**Marsja**, E., Marsh, J.E., Neely G., Hansson P., Ljungberg K.J. (2017, April). Domain-generality or domain-specificity of the short-term memory: insights from a multisensory distraction paradigm. Re-thinking the Senses Spring School, Dubrovnik, Croatia. **Poster**.

**Marsja**, E., Marsh, J.E., Neely G., Hansson P., Ljungberg K.J. (2016, September). Do Spatial Changes in Sounds and Vibrations Affect Visuo-spatial and Verbal Short-Term Memory? Attention and Control: Insights from Distraction, Workshop, University of Central Lancashire, Preston, UK. **Invited Talk**.

**Marsja**, E., Marsh, J.E., Neely G., Hansson P., Ljungberg K.J. (2016, June). Spatial Change in Multisensory Distractors Impact on Verbal and Spatial Short Term Memory. International Multisensory Research Forum 17^th^ annual meeting, Suzhou, CHN. **Oral presentation**.

**Marsja**, E., Neely G., Ma, L., Ljungberg K.J., (2015, August). Cross-modality matches of intensity and attention capture dimensions of auditory and vibrotactile stimuli. Fechner Day 2015. The 31^st^ Annual Meeting of the International Society for Psychophysics, Québec, CA. **Poster**.

**Marsja**, E., Neely, G., Parmentier, F.B.R., Ljungberg, K.J. (2014, October) Deviance Distraction Is Contingent on Stimuli Being Presented within the Same Modality. Psychonomic Society’s 55^th^ Annual Meeting. Long Beach, CA, USA. **Poster**.

Ljungberg, K.J., Parmentier, F.B.R., **Marsja**, E., Neely, G. Jones, D., (2014, January). Any Tom, Dick, or Harry will do: Hearing one’s own name distracts no more than any other in a cross-modal oddball task. Experimental Psychology Society Meeting. London, UK. **Poster**.

**Marsja**, E., Neely, G., Parmentier, F.B.R., Ljungberg, K.J. (2013, October). Maintenance of the distractive effect of deviating vibrotactile stimuli in a cross-modal oddball paradigm.  The 29^th^ Annual meeting of the International Society of Psychophysics, Freiburg, DE. **Poster**.

## Popular Science and Education-Related Articles

**Marsja**, E. (2016, July). Python Programming in Psychology – From Data Collection to Analysis. *JEPS Bulletin - The Official Blog of the Journal of European Psychology Students*. **Invited Blog Post**. Retrieved from
\sloppy
http://blog.efpsa.org/2016/07/12/python-programming-in-psychology-from-data-collection-to-analysis/

## Funding and Grants

**6000 SEK** from the Department of Psychology, Umeå University, for participating in the Re-thinking the Senses Spring School, Dubrovnik, Croatia, 2017.

**15000 SEK** from Lars Hiertas Minnesfond for the project *Är korttidsminnet domän-generellt eller domän-specifikt? (Is short-term memory domain-general or domain specific?)*, 2016.

**12 000 SEK** from the Faculty of Social sciences, Umeå University, for participating in the workshop Attention and Control: Insights from Distraction, and visiting a researcher at the University of Central Lancashire, Preston, UK, 2016. 

**8000 SEK** from the Department of Psychology, Umeå University, for participating the conference 17^th^ International Multisensory Research Forum 15-18 June, Souzou, China, 2016.

**10 000 SEK**  from JC Kempes minnesfond for the project *Is everyday distractibility related to attention capture by
vibrating deviants?*, 2014.

**9 000 SEK**  from Knut och Alice Wallenbergs Stiftelse for participating in the conferences Psychonomic Society’s 55^th^ Annual Meeting, 20-23 November, and APCAM, 20 November, Long Beach, USA, 2014. 

**6000 SEK** from the Department of Psychology for participating the conference Fechner Day 2013 (the 29^th^ Annual Meeting of the International Society for Psychophysics) 21-25 October, Freiburg i.Br., Germany, 2013.

## Peer-reviewed for Journals:

* Journal of Cognitive Psychology

Information about my responsibilities as a peer-reviewer can be found in my [Publons profile](https://www.publons.com/a/1517052/).

## Skills & Training

### Training

2017 Spring School *Re-Thinking the Senses*, Inter-University Centre, Dubrovnik, Croatia

### Teaching  

Primarily in:

* Cognitive Psychology (attention, perception, & working memory)
* Applied Cognitive Psychology (attention and perception)
* Research Methods & Basic Statistics

The majority of lectures, seminars, lab demonstrations, supervision of group project (both involving empirical and applied projects) and supervision of thesis' have been given at the Department of Psychology Umeå University, Sweden (2014 - 2017). I have also held workshops, and supervised projects at the Department of Behavioral Science and Learning, Linköping University (2019). At Umeå University and Linköping University, I have so far taught 950  and 44 clock hours, respectively. See Table 1 for an overview of my teaching responsibilities, clock hours, and courses.


### Supervision of Master students (graduate level)


Ma, L. (2015). Department of Psychology, Umeå University. "Cross-Modal Matching of Distractibility in Auditory and Tactile Stimuli". Master Thesis in Cognitive Science (15 ECTS).

Blide, M. (2014). Department of Psychology, Umeå University. "Att orka lämna ett misshandelsförhållande: Anknytningens beydelse (To cope leaving abusive relationships: The importance of attachment). Master Thesis in Clinical Psychology (30 ECTS).

### Teaching Workshops

Oct 2018\hspace{0.75cm}\textbf{R Workshop "Step-by-Step"}\vspace{1mm}

\hrule
\begin{changemargin}{2.15cm}{2.4cm}


Department of Psychology, Umeå University.

An introduction to R statistical programming language - presented to senior researchers with a focus on basic programming and the R environment.

\end{changemargin}

### Additional skills

* Extensive knowledge in statistical software such as SPSS, JASP, and R statistical programming environment
* Strong scripting skills in Python (v2.7.x & v3.x.x) and R
* Substantial skills in programming and performing experiments using both E-prime and Python (i.e., PsychoPy, OpenSesame, & Expyriment)
* Good skills in Microsoft Word and Excel
* Basic programming skills in Visual Basic, E-basic (E-prime), MATLAB, Bash, JavaScript, and PHP
* Basic skills in Markdown (e.g., RMarkdown) and \LaTeX

### Responsibilities

* Elected chairperson of the Ph.D. students Council of the Department of Psychology, Umeå University.


\begin{landscape}
\pagestyle{empty}

```{r, echo=FALSE, message=FALSE, results='hide', warning=FALSE}

rm(list=ls())
library(stargazer)
require(xtable)

 datadir = "./Data/teachinghours.csv"


insertRow <- function(existingDF, newrow, r) {
  existingDF[seq(r+1,nrow(existingDF)+1),] <- existingDF[seq(r,nrow(existingDF)),]
  existingDF[r,] <- newrow
  existingDF
}
t.hours <- read.csv(datadir, sep = ';', row.names=NULL)
t.hours$Period <- with(t.hours, paste(Semester, Year, sep=' '))

table.data <- cbind(t.hours[9], t.hours[6], t.hours[5], t.hours[3], t.hours[1], t.hours[7:8])
table.data <- table.data[table.data$Type != 'NOT HELD YET',]
dups <- duplicated(table.data[,1]) | duplicated(table.data[,1])
table.data[which(dups),]$Period <- ' '

total.teaching <- sum(table.data$Clock.Hours)

#Creating empty rows.. i hope
idx.dups <- which(!dups[-1])
idx.adder <- 0
for(index in 1:length(idx.dups)){
  row <-idx.dups[index]+idx.adder
  ifelse(index == 1, newdata <- table.data, newdata <- newdata)
  newdata <- insertRow(newdata, ' ',row+1)
  idx.adder = idx.adder + 1
}

a <- stargazer(newdata, style = "aer", title='Teaching responsibilities - an overview of type of teaching, hours, etc.', notes= paste(' Total of clock hours:', total.teaching, ', UG = Undergraduate, G = Graduate, VT = Spring term, HT = autumn term', sep = ' '), summary=FALSE, rownames=FALSE, font.size="tiny")

```
{

```{r, echo=FALSE, results='asis'}
collapse <- function(st) paste(st, collapse="")
st <- gsub(collapse(rep("c", 7)), collapse(rep("l",7)), a)
st <- gsub('lllllll\\} ', 'lp\\{4cm\\}p\\{4cm\\}lp\\{5cm\\}ll\\} ', st)

st <- gsub('Clock.Hours', 'Clock Hours ', st)
st <- gsub('Course.and.Program', 'Course/Program', st)

st[2:3] <- ''
cat(st)
```
}
\end{landscape}
