\documentclass[]{article}
\usepackage{pdflscape}

\usepackage{everypage}

\newcommand{\Lpagenumber}{\ifdim\textwidth=\linewidth\else\bgroup
  \dimendef\margin=0 %use \margin instead of \dimen0
  \ifodd\value{page}\margin=\oddsidemargin
  \else\margin=\evensidemargin
  \fi
  \raisebox{\dimexpr -\topmargin-\headheight-\headsep-0.5\linewidth}[0pt][0pt]{%
    \rlap{\hspace{\dimexpr \margin+\textheight+\footskip}%
    \llap{\rotatebox{90}{ CV  - Erik Marsja 
- \thepage\hspace{1pt}(\pageref{LastPage})}}}}%
\egroup\fi}
\AddEverypageHook{\Lpagenumber}%

\usepackage{adjustbox}
\usepackage{titling}
\usepackage{caption}
\usepackage{tabularx}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{titlesec}
\usepackage[scaled=.90]{helvet}% Helvetica, served as a model for arial

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0.0pt}
\fancyfoot[CO,CE]{  CV -   Erik Marsja -  \thepage\hspace{1pt}(\pageref{LastPage})}
\fancypagestyle{plain}{\pagestyle{fancy}}

\usepackage[margin=1.2in]{geometry}

% Font awesome
\usepackage{fontawesome}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

% For tables


% Tightlist

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% URLS
\usepackage[hidelinks]{hyperref}
\usepackage{breakurl}
\usepackage{float} % here for H placement parameter

% Appendix header style

\fancypagestyle{style2}{
\fancyhf{}
\fancyhead[C]{Appendix 1}
}


% For Changing the margins (Education)

\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist 

%For displaying the table in landscape format
\usepackage[absolute]{textpos}

\fancypagestyle{lscape}{% 
\fancyhf{} % clear all header and footer fields 
\fancyfoot[LE]{%
\begin{textblock}{20}(1,5){\rotatebox{90}{\leftmark}}\end{textblock}
\begin{textblock}{1}(13,10.5){\rotatebox{90}{\thepage}}\end{textblock}}
\fancyfoot[LO] {%
\begin{textblock}{1}(13,10.5){\rotatebox{90}{\thepage}}\end{textblock}
\begin{textblock}{20}(1,13.25){\rotatebox{90}{\rightmark}}\end{textblock}}
\renewcommand{\headrulewidth}{0pt} 
\renewcommand{\footrulewidth}{0pt}}

\setlength{\TPHorizModule}{1cm}
\setlength{\TPVertModule}{1cm}

% Appendix
\fancypagestyle{style2}{
\fancyhf{}
\fancyhead[C]{Appendix 1}
\renewcommand{\headrulewidth}{1pt}
}



\newcommand\secbar {
    \tikz[baseline, trim left=3.2cm] 
    {
        \fill [white] (3cm,0.1ex) rectangle +(0.2cm,1.1ex);
        \draw [gray!95, fill=gray!80] (0cm,0.1ex) rectangle (3cm,1.1ex);        
    }
}
\newcommand\subsecbar {
    \tikz[baseline, trim left=0.15cm] 
    {
        \fill [white] (2cm,0.1ex) rectangle +(0.2cm,1.1ex);
        \fill [blue!40] (0cm,0.1ex) rectangle (2cm,1.1ex);      
    }
}

\newcommand\subsubsecbar {
    \tikz[baseline, trim left=0.15cm] 
    {
        \fill [white] (1cm,0.1ex) rectangle +(0.2cm,1.1ex);
        \fill [blue!40] (0cm,0.1ex) rectangle (2cm,1.1ex);      
    }
}

\titleformat{\section}{\large}{}{0cm}{\secbar}
\titleformat{\subsection}{\large}{}{0cm}{\normalfont\sffamily\Large\bfseries\subsecbar}
\titleformat{\subsubsection}{}{}{0cm}{\normalfont\sffamily\large\bfseries}

% No first line paragraph indent
\usepackage{parskip}
\usepackage{enumitem}


\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}
\titlespacing\subsubsection{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}

\newcolumntype{Y}{>{\centering\arraybackslash}X}

\begin{document}

\centerline{\huge \textbf{Erik Marsja, Ph.D.} | \textcolor{darkgray}{Curriculum Vitae}}

\vspace{2 mm}

\hrule

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{@{}lYl@{}}
\textbf{Home Address}: & &  \textbf{Personal Identity Number:} 
\\Tvistevägen 26, SE-907 36 Umeå, Sweden & &  19810526-8935 
\\\\

 \faPhone \hspace{1 mm}  +4613-28 22 85  \hspace{1 mm}  &  & \faEnvelopeO \hspace{1 mm} \href{mailto:}{\tt \href{mailto:erik.marsja@liu.se}{\nolinkurl{erik.marsja@liu.se}}} \hspace{1 mm}  \\
 \faGlobe \hspace{1 mm} \href{http://www.marsja.se}{\tt www.marsja.se}   &  & \faGithub \hspace{1 mm} \href{http://github.com/marsja}{\tt marsja} \hspace{1 mm}  \\
 \multicolumn{3}{c}{}
 \\\hline
\end{tabularx}
\end{table}

\hypertarget{degrees-and-titles}{%
\subsection{Degrees and Titles}\label{degrees-and-titles}}

2017 \hspace{1.5cm} \textbf{Ph.D. in Psychology}\vspace{1mm}

\hrule

\begin{changemargin}{2.3cm}{2.4cm}

Department of Psychology, Umeå University.

\textbf{Thesis title}: Attention capture by sudden and unexpected changes: a multisensory perspective. 

Available from the DiVA Database: \sloppy http://umu.diva-portal.org/smash/record.jsf?pid=diva2%3A1156775

\textbf{Supervisors}: Associate Professor Jessica K. Ljungberg, Professor Gregory Neely, \& Dr. Patrik Hansson
\end{changemargin}

2012 \hspace{1.5cm}\textbf{M.Sc. in Cognitive Science}\vspace{1mm}

\hrule
\begin{changemargin}{2.3cm}{2.4cm}

Department of Psychology, Umeå University.

\textbf{Thesis title}: Attention Capture: The Impact of Change in Spatial Sound Source on Behavior. 
    
\textbf{Supervisor}: Associate Professor Jessica K. Ljungberg
\end{changemargin}

2011 \hspace{1.5cm}\textbf{B.Sc. in Cognitive Science}\vspace{1mm}

\hrule

\begin{changemargin}{2.3cm}{2.4cm}

Department of Psychology, Umeå University.

\textbf{Thesis title}:  Attention Capture: Studying the Distracting Effect of One’s Own Name.

Available from DiVA Database: \sloppy http://urn.kb.se/resolve?urn=urn:nbn:se:umu:diva-46607.
    
\textbf{Supervisor}: Associate Professor Jessica K. Ljungberg
\end{changemargin}

\hypertarget{academic-positions}{%
\subsection{Academic Positions}\label{academic-positions}}

Jan 2019 - \hspace{0.50cm}\textbf{Postdoctoral Researcher}\vspace{1mm}

\hrule
\begin{changemargin}{2.3cm}{2.4cm}

Division for Disability Resarch, Department of Behavioural Sciences and Learning (IBL), Linköping University.

Analysing data from a large database (i.e., n200) and preparing manuscripts in the field of cognitive hearing science. Acquiring expertise in hearing loss, aging, and cognitive functioning. Responsible for arranging the monthly \href{https://liu.se/linnecentrum-head/en}{HEAD} seminar series. This includes contacting and inviting national, and international, researchers, booking flights, hotels, as well as setting up equipment for online streaming.

\end{changemargin}

Aug 2018 -

Oct
2018\hspace{0.75cm}\textbf{Postdoctoral Research Assistant}\vspace{1mm}

\hrule
\begin{changemargin}{2.3cm}{2.4cm}

Department of Psychology, Umeå University.

\textbf{Project}: How does humans perception of safety differ in a broken communication chain compared to an unbroken communication chain? 

Literature study commissioned by SOS Alarm, an emergency agency (e.g., public-safety answering point), with the results disseminating in a report as well as an oral presentation for leaders in SOS Alarm's organisation.

\end{changemargin}

Oct 2012 -

June
2018\hspace{0.75cm}\textbf{PhD Student and Teaching Assistant}\vspace{1mm}

\hrule
\begin{changemargin}{2.3cm}{2.4cm}

Department of Psychology, Umeå University.

Planning of studies, programming of experiments, literature search, data analysis, scientific communication, and many more. See the section "Teaching responsibilities" for an overview of my pedagogical experience.

\end{changemargin}

June
2011\hspace{0.75cm}\textbf{Undergrad. Research Assistant}\vspace{1mm}

\hrule
\begin{changemargin}{2.3cm}{2.4cm}

Department of Psychology, Umeå University.

Recruitment of participants and data collection.

\end{changemargin}

\hypertarget{non-academic-positions}{%
\subsection{Non-Academic Positions}\label{non-academic-positions}}

April 2007 -

Aug
2009\hspace{0.75cm}\textbf{Heavy (Steel) Industry Worker}\vspace{1mm}

\hrule
\begin{changemargin}{2.3cm}{2.4cm}

Plannja AB, Luleå.

Manufacturing of roof panels, sheet metal and roof protection, packaging of the
finished products and some warehouse work including truck driving. 

\end{changemargin}

\hypertarget{publications}{%
\subsection{Publications}\label{publications}}

\hypertarget{international-peer-reviewed-journals}{%
\subsubsection{International peer-reviewed
journals}\label{international-peer-reviewed-journals}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Rosa, E., \textbf{Marsja}, E., \& Ljungberg, J. K. (2020). Exploring
  Residual Capacity: The Effectiveness of a Vibrotactile Warning During
  Increasing Levels of Mental Workload in Simulated Flight Tasks.
  \emph{Aviation Psychology and Applied Human Factors, 10(1)}, 13--23.
  \url{https://doi.org//10.1027/2192-0923/a000180}
\item
  \textbf{Marsja}, E., Marsh, J.E., Hansson, P., \& Neely, G. (2019).
  Examining the Role of Spatial Changes in Bimodal and Uni-Modal
  To-Be-Ignored Stimuli and How They Affect Short-Term Memory Processes.
  \emph{Frontiers In Psychology}.
  \url{https://doi.org/10.3389/fpsyg.2019.00299}
\item
  \textbf{Marsja}, E., Neely, G., \& Ljungberg, K.J. (2018).
  Investigating Deviance Distraction and the Impact of the Modality of
  the To-Be-Ignored Stimuli. \emph{Experimental Psychology, 65(2)},
  61--70. \url{http://doi.org/10.1027/1618-3169/a000390}
\item
  Ljungberg, K. J., Parmentier, F. B. R., Jones, D. M., \textbf{Marsja},
  E., \& Neely, G. (2014). ``What's in a name?'' ``No more than when
  it's mine own''. Evidence from auditory oddball distraction.
  \emph{Acta Psychologica, 150C}, 161--166.
  \url{http://dx.doi.org/10.1016/j.actpsy.2014.05.009}
\end{enumerate}

\hypertarget{publications-in-preparationsubmittedunder-revision}{%
\subsubsection{Publications In Preparation/Submitted/Under
Revision}\label{publications-in-preparationsubmittedunder-revision}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Stenbäck, V., \textbf{Marsja}, E., Hällgren, M., Lyxell, B., \&
  Larsby, B. (Submitted). The contribution of age, working memory
  capacity and inhibitory control on speech-recognition-in-noise in
  young, and older adult listeners.
\item
  Stenbäck, V., \textbf{Marsja}, Ellis, R., \& Rönnberg, J. (Under
  Revision). Relationships between objective and subjective outcome
  measures of speech recognition in noise.
\item
  \textbf{Marsja}, E., Stenbäck, V., Moradi, S., Danielsson, H., \&
  Rönnberg, J. (Manuscript in Preparation). Examining the Relationship
  Among Aging, Hearing, Cognitive Functioning, and Speech in Noise
  Performance using Structural Equation Modeling.
\item
  \textbf{Marsja}, E. Elbe, P., \& Sörman, D.E. (Manuscript in
  Preparation). Examining the Factor Structure of the Swedish
  Translation of the Attentional Control Scale and it's relation to
  objective measures of attention.
\item
  Marsh, J.E., Vachon, F., Sörqvist, P., \textbf{Marsja}, E., Röer J.P.,
  \& Ljungberg, K.J. (Manuscript in Preparation). Irrelevant
  vibro-tactile stimuli produce a changing-state effect: Implications
  for theories of interference in short-term memory.
\item
  \textbf{Marsja}, E., Neely, G., \& Ljungberg, K.J (Manuscript in
  Preparation). Deviance distraction in the auditory and tactile
  modalities after repeated exposure: differential aspects of tactile
  and auditory deviants.
\end{enumerate}

\hypertarget{conference-presentations}{%
\subsection{Conference Presentations}\label{conference-presentations}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Marsja}, E., Danielsson, H., Stenbäck, V., Moradi, S.,
  Rönnberg, J. (2019, November). Examining how Cognitive Functioning,
  Aging, and Hearing Loss, Affect Speech-in-Noise Performance. Aging and
  Speech Communication conference, Tampa, Florida, USA. \textbf{Poster}.
\item
  Stenbäck, V., \textbf{Marsja}, E., Danielsson, H., Rönnberg, J. (2019,
  November). Logical and Auditory Inference Making: Performance in the
  HINT in normally-hearing and hearing-impaired listeners. Aging and
  Speech Communication conference, Tampa, Florida, USA. \textbf{Poster}.
\item
  Bampouni, E., \textbf{Marsja}, E., Sörman, D.E., \& Ljungberg, K.J
  (2019, November). Do Action Gamers Have Enhanced Visual Search Skills?
  a Realistic Task Approach. The 15th SweCog conference of the Swedish
  Cognitive Science Society, Umeå, Sweden. \textbf{Poster}.
\item
  \textbf{Marsja}, E., Danielsson, H., Stenbäck, V., Moradi, S., \&
  Rönnberg, J. (2019, June). Examining Relationship Amongst Cognition,
  Hearing Loss, Age, \& Speech in Noise. Cognitive Hearing Science for
  Communication, Linköping, Sweden. \textbf{Poster}.
\item
  Stenbäck, V., Moradi, S., \textbf{Marsja}, E., Danielsson, H., \&
  Rönnberg, J. (2019, June). Logical and auditory inference-making in
  normally-hearing and hearing-impaired listeners. Cognitive Hearing
  Science for Communication, Linköping, Sweden. \textbf{Poster}.
\item
  \textbf{Marsja}, E., Marsh, J.E., Neely G., Hansson P., \& Ljungberg
  K.J. (2017, April). Domain-generality or domain-specificity of the
  short-term memory: insights from a multisensory distraction paradigm.
  Re-thinking the Senses Spring School, Dubrovnik, Croatia.
  \textbf{Poster}.
\item
  \textbf{Marsja}, E., Marsh, J.E., Neely G., Hansson P., \& Ljungberg
  K.J. (2016, September). Do Spatial Changes in Sounds and Vibrations
  Affect Visuo-spatial and Verbal Short-Term Memory? Attention and
  Control: Insights from Distraction, Workshop, University of Central
  Lancashire, Preston, UK. \textbf{Invited Talk}.
\item
  \textbf{Marsja}, E., Marsh, J.E., Neely G., Hansson P., \& Ljungberg
  K.J. (2016, June). Spatial Change in Multisensory Distractors Impact
  on Verbal and Spatial Short Term Memory. International Multisensory
  Research Forum 17\textsuperscript{th} annual meeting, Suzhou, CHN.
  \textbf{Oral presentation}.
\item
  \textbf{Marsja}, E., Neely G., Ma, L., \& Ljungberg K.J., (2015,
  August). Cross-modality matches of intensity and attention capture
  dimensions of auditory and vibrotactile stimuli. Fechner Day 2015. The
  31\textsuperscript{st} Annual Meeting of the International Society for
  Psychophysics, Québec, CA. \textbf{Poster}.
\item
  \textbf{Marsja}, E., Neely, G., Parmentier, F.B.R., \& Ljungberg, K.J.
  (2014, October) Deviance Distraction Is Contingent on Stimuli Being
  Presented within the Same Modality. Psychonomic Society's
  55\textsuperscript{th} Annual Meeting. Long Beach, CA, USA.
  \textbf{Poster}.
\item
  Ljungberg, K.J., Parmentier, F.B.R., \textbf{Marsja}, E., Neely, \& G.
  Jones, D., (2014, January). Any Tom, Dick, or Harry will do: Hearing
  one's own name distracts no more than any other in a cross-modal
  oddball task. Experimental Psychology Society Meeting. London, UK.
  \textbf{Poster}.
\item
  \textbf{Marsja}, E., Neely, G., Parmentier, F.B.R., \& Ljungberg, K.J.
  (2013, October). Maintenance of the distractive effect of deviating
  vibrotactile stimuli in a cross-modal oddball paradigm. The
  29\textsuperscript{th} Annual meeting of the International Society of
  Psychophysics, Freiburg, DE. \textbf{Poster}.
\end{enumerate}

\hypertarget{popular-science-and-education-related-articles}{%
\subsection{Popular Science and Education-Related
Articles}\label{popular-science-and-education-related-articles}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Marsja}, E. (2016, July). Python Programming in Psychology --
  From Data Collection to Analysis. \emph{JEPS Bulletin - The Official
  Blog of the Journal of European Psychology Students}. \textbf{Invited
  Blog Post}. Retrieved from \sloppy
  \url{http://blog.efpsa.org/2016/07/12/python-programming-in-psychology-from-data-collection-to-analysis/}
\end{enumerate}

\hypertarget{funding-and-grants}{%
\subsection{Funding and Grants}\label{funding-and-grants}}

\textbf{6000 SEK} from the Department of Psychology, Umeå University,
for participating in the Re-thinking the Senses Spring School,
Dubrovnik, Croatia, 2017.

\textbf{15000 SEK} from Lars Hiertas Minnesfond for the project \emph{Är
korttidsminnet domän-generellt eller domän-specifikt? (Is short-term
memory domain-general or domain specific?)}, 2016.

\textbf{12 000 SEK} from the Faculty of Social sciences, Umeå
University, for participating in the workshop Attention and Control:
Insights from Distraction, and visiting a researcher at the University
of Central Lancashire, Preston, UK, 2016.

\textbf{8000 SEK} from the Department of Psychology, Umeå University,
for participating the conference 17\textsuperscript{th} International
Multisensory Research Forum 15-18 June, Souzou, China, 2016.

\textbf{10 000 SEK} from JC Kempes minnesfond for the project \emph{Is
everyday distractibility related to attention capture by vibrating
deviants?}, 2014.

\textbf{9 000 SEK} from Knut och Alice Wallenbergs Stiftelse for
participating in the conferences Psychonomic Society's
55\textsuperscript{th} Annual Meeting, 20-23 November, and APCAM, 20
November, Long Beach, USA, 2014.

\textbf{6000 SEK} from the Department of Psychology for participating
the conference Fechner Day 2013 (the 29\textsuperscript{th} Annual
Meeting of the International Society for Psychophysics) 21-25 October,
Freiburg i.Br., Germany, 2013.

\hypertarget{peer-reviewed-for-journals}{%
\subsection{Peer-reviewed for
Journals:}\label{peer-reviewed-for-journals}}

\begin{itemize}
\tightlist
\item
  Journal of Cognitive Psychology
\item
  Frontiers of Psychology
\item
  Behavior Research Methods
\end{itemize}

\hypertarget{skills-training}{%
\subsection{Skills \& Training}\label{skills-training}}

\hypertarget{training}{%
\subsubsection{Training}\label{training}}

2017 Spring School \emph{Re-Thinking the Senses}, Inter-University
Centre, Dubrovnik, Croatia

\hypertarget{teaching}{%
\subsubsection{Teaching}\label{teaching}}

Primarily in:

\begin{itemize}
\tightlist
\item
  Research Methods \& Statistical Methods
\item
  Cognitive Psychology (attention, perception, \& working memory)
\item
  Applied Cognitive Psychology (attention and perception)
\end{itemize}

The majority of lectures, seminars, lab demonstrations, supervision of
group project (both involving empirical and applied projects) and
supervision of thesis' have been given at the Department of Psychology
Umeå University, Sweden (2014 - 2017). I have also held lectures,
seminars, and supervised projects and thesis' at the Department of
Behavioral Science and Learning and Department of Computer and
Information Science, Linköping University (2019 - ). At Umeå University
and Linköping University, I have so far taught 950 and 550 clock hours,
respectively.

\hypertarget{supervision-of-bachelor-students-undergraduate-level}{%
\paragraph{Supervision of Bachelor Students (Undergraduate
Level)}\label{supervision-of-bachelor-students-undergraduate-level}}

\begin{itemize}
\item
  Lindberg, F. (2020). Department of Computer and Information Science,
  Linköping University. ``Hur ungas attityder kring hörselnedsättningar
  orsakade av fritidsbuller påverkas av deras koppling till sitt
  framtida jag.'' (How young people's attitudes to hearing impairments
  caused by leisure noise are affected by their connection to their
  future selves.) Bachelor's Thesis in Cognitive Science (18 ECTS).
  \emph{Main supervisor}
\item
  Dahlgren, S. (2020).Department of Computer and Information Science,
  Linköping University. "Self-determination perceived by users in
  support services pursuant to LSS - An analysis on a municipal level.
  Bachelor's Thesis in Cognitive Science (18 EcTS). \emph{Main
  supervisor}
\item
  Rombo, A. (2020). Department of Computer and Information Science,
  Linköping University. ``The association between cognition and
  speech-in-noise perception - Investigating the link between
  speech-in-noise perception and fluid intelligence in people with and
  without hearing loss.'' Bachelor's Thesis in Cognitive Science (18
  ECTS). \emph{Main supervisor}
\end{itemize}

\hypertarget{supervision-of-master-students-graduate-level}{%
\paragraph{Supervision of Master Students (Graduate
Level)}\label{supervision-of-master-students-graduate-level}}

\begin{itemize}
\item
  Carlbring, J. (2020) Department of Computer and Information Science,
  Linköping University. ``Inclusive Design for Mobile Devices with WCAG
  and Attentional Resources in Mind.'' Master's Theis in Cognitive
  Science (30 ECTS). \emph{Main supervisor}
\item
  Ma, L. (2015). Department of Psychology, Umeå University.
  ``Cross-Modal Matching of Distractibility in Auditory and Tactile
  Stimuli''. Master's Thesis in Cognitive Science (15 ECTS).
  \emph{Co-superviser}
\item
  Blide, M. (2014). Department of Psychology, Umeå University. "Att orka
  lämna ett misshandelsförhållande: Anknytningens beydelse (To cope
  leaving abusive relationships: The importance of attachment). Master's
  Thesis in Clinical Psychology (30 ECTS). \emph{Co-supervisor}
\end{itemize}

\hypertarget{teaching-workshops}{%
\subsubsection{Teaching Workshops}\label{teaching-workshops}}

Oct 2018\hspace{0.75cm}\textbf{R Workshop "Step-by-Step"}\vspace{1mm}

\hrule
\begin{changemargin}{2.15cm}{2.4cm}

Department of Psychology, Umeå University.

An introduction to R statistical programming language - presented to senior researchers with a focus on basic programming and the R environment.

\end{changemargin}

\hypertarget{additional-skills}{%
\subsubsection{Additional skills}\label{additional-skills}}

\begin{itemize}
\tightlist
\item
  Extensive knowledge in statistical software such as SPSS, JASP,
  Jamovi, and R statistical programming environment
\item
  Strong scripting skills in Python (v2.7.x \& v3.x.x) and R
\item
  Substantial skills in programming and performing experiments using
  both E-prime and Python (i.e., PsychoPy, OpenSesame, \& Expyriment)
\item
  Good skills in Microsoft Word and Excel
\item
  Basic programming skills in Visual Basic, E-basic (E-prime), MATLAB,
  Bash, JavaScript, and PHP
\item
  Basic skills in Markdown (e.g., RMarkdown) and \LaTeX
\end{itemize}

\hypertarget{responsibilities}{%
\subsubsection{Responsibilities}\label{responsibilities}}

\begin{itemize}
\tightlist
\item
  Elected chairperson of the Ph.D.~students Council of the Department of
  Psychology, Umeå University.
\end{itemize}

\end{document}