---
title: "Erik Marsja"
output:
  pdf_document:
    includes:
      after_body: doc_suffix.tex
      in_header: header.tex
    keep_tex: yes
  html_document:
    css: cv.css
  word_document: default
date: '`r Sys.Date()`'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
<br>
<br>

+-------------------------------------------------+--------------------------------------+------------------------------------------------+
| **Telephone**:\                                 | **Mobile**:\                         | **Email**: erik.marsja@umu.se\                 |
| +46 90 786 79 59                                | +46 70363 36 62                      | **Web**:    http://www.marsja.se               |
+=================================================+======================================+================================================+
| **University adress**:                          |                                      | **Home adress**:                               |
+-------------------------------------------------+--------------------------------------+------------------------------------------------+
| Department of Psychology\                       |                                      | Kandidatvägen 1\                               |
| Umeå University, SE-901 87, Umeå,               |                                      | SE-907 33 Umeå, \                              |
| Sweden                                          |                                      | Sweden                                         |
+-------------------------------------------------+--------------------------------------+------------------------------------------------+

## Current research

\hrule
I am examining how sudden and unexpected changes in our environment captures our attention and, thus, causes distraction from what we currently are engaged in. Specifically, my Ph.D. work is examining how sudden and unexpected changes in auditory, tactile, and the combination of both auditory and tactile (multisensory) stimulation affects performance in speeded and short-term memory tasks. 

## Research ambition

\hrule
My goal is to create my academic career in cognitive psychology. Mainly doing ground research but also more applied (e.g., multisensory alarms). Specifically, in the areas of attention and cognitive control. I aspire to eventually be able to work as an established researcher in these, and related, areas  (i.e., cognitive neuroscience). 

## Education and Degrees	

\hrule

* 2012-Present	Ph.D. Student in Psychology 

* 2011-2012	M.Sc. in Cognitive Science (*Thesis*: Attention Capture: The Impact of Change in Spatial Sound Source on Behavior- Department of Psychology, Umeå University.

* 2008-2011	B.Sc. in Cognitive Science (*Thesis*:  Attention Capture: Studying the Distracting Effect of One’s Own Name. Department of Psychology, Umeå University. Available from DiVA Database (http://urn.kb.se/resolve?urn=urn:nbn:se:umu:diva-46607).

## Publications
\hrule

### International peer-reviewed journals
\hrule

Ljungberg, K. J., Parmentier, F. B. R., Jones, D. M., **Marsja**, E., & Neely, G. (2014). “What’s in a name?” “No more than when it’s mine own". Evidence from auditory oddball distraction. Acta Psychologica, 150C, 161–166. doi:10.1016/j.actpsy.2014.05.009.

### Publications In Preparation/Submitted/Under Revision

\hrule

Rosa, E., **Marsja**, E., Ljungberg K.J. (In Preparation). Vibrotactile On-thigh Alarm Detection as a Function of Flight Task Mental Workload.

**Marsja**, E., Neely, G., Ljungberg K.J. (Under revision). Investigating deviance distraction and the impact of the modality of the to-be-ignored stimuli.
 
Marsh, J.E., Sörqvist, P., **Marsja**, E., Röer J.P., & Ljungberg, K.J. (Submitted).  Irrelevant vibro-tactile stimuli produce a changing-state effect: Implications for theories of interference in short-term memory.

**Marsja**, E., Neely, Ljungberg, K.J (Under revision). Deviance distraction in the auditory and tactile modalities after repeated exposure: differential aspects of tactile and auditory deviants.

## Current research collaborations

\hrule

* Associate Professor Jessica K. Ljungberg, Department of Psychology, Umeå University, Umeå, Sweden
* Professor Gregory Neely, Department of Psychology, Umeå University, Umeå, Sweden
* Dr. Patrik Hansson, Department of Psychology, Umeå University, Umeå, Sweden 
* Dr. John E. Marsh, School of Psychology, University of Central Lancashire, UK
* Professor Patrik Sörqkvist, Faculty of Engineering and Sustainable Development, Högskolan i Gävle, Gävle

## Conference Presentations

\hrule


**Marsja**, E., Marsh, J.E., Neely G., Hansson P., Ljungberg K.J., (2017, April). Domain-generality or domain-specificity of the short-term memory: insights from a multisensory distraction paradigm. Re-thinking the Senses Spring School, Dubrovnik, Croatia. **Poster**.

**Marsja**, E., Marsh, J.E., Neely G., Hansson P., Ljungberg K.J., (2016, September). Do Spatial Changes in Sounds and Vibrations Affect Visuo-spatial and Verbal Short-Term Memory? Attention and Control: Insights from Distraction, Workshop, University of Central Lancashire, Preston, UK. **Invited Talk**.

**Marsja**, E., Marsh, J.E., Neely G., Hansson P., Ljungberg K.J., (2016, June). Spatial Change in Multisensory Distractors Impact on Verbal and Spatial Short Term Memory. International Multisensory Research Forum 17^th^ annual meeting, Suzhou, CHN. **Oral presentation**.

**Marsja**, E., Neely G., Ma, L., Ljungberg K.J., (2015, August). Cross-modality matches of intensity and attention capture dimensions of auditory and vibrotactile stimuli. Fechner Day 2015. The 31^st^ Annual Meeting of the International Society for Psychophysics, Québec, CA. **Poster**.

**Marsja**, E., Neely, G., Parmentier, F.B.R., Ljungberg, K.J., (2014, October) Deviance Distraction Is Contingent on Stimuli Being Presented within the Same Modality. Psychonomic Society’s 55^th^ Annual Meeting. Long Beach, CA, USA. **Poster**.

Ljungberg, K.J., Parmentier, F.B.R., **Marsja**, E., Neely, G., Jones, D., (2014, January). Any Tom, Dick, or Harry will do: Hearing one’s own name distracts no more than any other in a cross-modal oddball task. Experimental Psychology Society Meeting. London, UK. **Poster**.

**Marsja**, E., Neely, G., Parmentier, F.B.R., Ljungberg, K.J., (2013, October). Maintenance of the distractive effect of deviating vibrotactile stimuli in a cross-modal oddball paradigm.  the 29^th^ Annual meeting of the International Society of Psychophysics, Freiburg, DE. **Poster**.

## Funding and Grants

\hrule

**15000 SEK** from Lars Hiertas Minnesfond for the project *Är korttidsminnet domän-generellt eller domän-specifikt? (Is short-term memory domain-general or domain specific?)*, 2016.

**8000 SEK** from the Department of Psychology for participating the conference 17^th^ International Multisensory Research Forum 15-18 June, Souzou, China, 2016.

**10 000 SEK**  from JC Kempes minnesfond for the project *Is everyday distractibility related to attention capture by
vibrating deviants?*, 2014.

**9 000 SEK**  from Knut och Alice Wallenbergs Stiftelse for participating in the conferences Psychonomic Society’s 55^th^ Annual Meeting, 20-23 November, and APCAM, 20 November, Long Beach, USA, 2014. 

**6000 SEK** from the Department of Psychology for participating the conference Fechner Day 2013 (the 29^th^ Annual Meeting of the International Society for Psychophysics) 21-25 October, Freiburg i.Br., Germany, 2013.

\newpage

## Teaching responsibilities
\hrule

### Past & current areas at undergraduate level

\hrule

Primarily in:

* Attention
* Perception
* Applied Cognitive Psychology
* Cognitive Psychology
* Research Methods
* Project work

Lectures, seminars, lab demonstrations, supervision of group project (both involving empirical and applied projects) and supervision of thesis' have been given at the Department of Psychology Umeå University, Sweden. I have so far taught 695 clock hours. See Table for an overview of teaching topics. 

\blandscape

```{r, echo=FALSE, message=FALSE, results='hide', warning=FALSE}

rm(list=ls())
library(stargazer)
require(xtable)

#If on Linux:
if(Sys.getenv("OS") == "Windows_NT"){ datadir = "C:/Users/erkmaa04/Dropbox/BetweenComps/timmar_undervisning/teachinghours.csv"
}else  { datadir = "~/Dropbox/BetweenComps/timmar_undervisning/teachinghours.csv"
}

insertRow <- function(existingDF, newrow, r) {
  existingDF[seq(r+1,nrow(existingDF)+1),] <- existingDF[seq(r,nrow(existingDF)),]
  existingDF[r,] <- newrow
  existingDF
}
t.hours <- read.csv(datadir)
t.hours$Period <- with(t.hours, paste(Semester, Year, sep=' '))

table.data <- cbind(t.hours[9], t.hours[6], t.hours[5], t.hours[3], t.hours[1], t.hours[7:8])
table.data <- table.data[table.data$Type != 'NOT HELD YET',]
dups <- duplicated(table.data[,1]) | duplicated(table.data[,1])
table.data[which(dups),]$Period <- ' '

total.teaching <- sum(table.data$Clock.Hours)

#Creating empty rows.. i hope
idx.dups <- which(!dups[-1])
idx.adder <- 0
for(index in 1:length(idx.dups)){
  row <-idx.dups[index]+idx.adder
  ifelse(index == 1, newdata <- table.data, newdata <- newdata)
  newdata <- insertRow(newdata, ' ',row+1)
  idx.adder = idx.adder + 1
}

a = stargazer(newdata, title='Teaching responsibilities - an overview of type of teaching, hours, etc.', notes= paste(' Total of clock hours:', total.teaching, 'UG = Undergraduate, G = Graduate', sep = ' '),  summary=FALSE, rownames=FALSE, font.size="small")

```

```{r, echo=FALSE, results='asis'}
collapse <- function(st) paste(st, collapse="")
st <- gsub(collapse(rep("c", 7)), collapse(rep("l",7)), a)
st <- gsub('lllllll\\} ', 'lp\\{4cm\\}p\\{4cm\\}lp\\{5cm\\}ll\\}', st)
st <- gsub('Clock.Hours', 'Clock Hours ', st)
st <- gsub('Course.and.Program', 'Course/Program', st)

st[2:3] <- ''
cat(st)
```

\elandscape

### Supervision of master students
\hrule

Ma, L. (2015). Department of Psychology, Umeå University. "Cross-Modal Matching of Distractibility in Auditory and Tactile Stimuli". Master Thesis in Cognitive Science (15 ECTS).

Blide, M. (2014). Department of Psychology, Umeå University. "Att orka lämna ett misshandelsförhållande: Anknytningens beydelse (To cope leaving abusive relationships: The importance of attachment). Master Thesis in Clinical Psychology (30 ECTS).


## Additional skills
\hrule

* Good skills in Microsoft Word and Excel
* Good skills in statistical software such as SPSS and R
* Good programming skills in Python (v2.7.x) and R
* Basic skills in Markdown (i.e., RMarkdown) and \LaTeX
* Basic programming skills in Visual Basic, E-basic (E-prime), and MATLAB
* Programming and performing experiments using both E-prime, MATLAB, and Python (i.e., PsychoPy & Expyriment)
